
## Make up a Seurat object with B6 and BALBC cells, then strip it down so I can save off a tiny file
```{r}
#| eval: false
library(Seurat)
library(rrrSingleCellUtils)
library(tidyverse)
merged_mouse <-
  merge(
    qs::qread("../../../24_validate_snvs/output/seurat_objects/individual/S0066_mouse.qs"),
    qs::qread("../../../24_validate_snvs/output/seurat_objects/individual/S0074_mouse.qs")
  ) %>%
  JoinLayers() %>%
  process_seurat()

merged_mouse@graphs <- list()
merged_mouse@assays$RNA@layers$counts <- NULL
merged_mouse@assays$RNA@layers$data <- NULL
merged_mouse@assays$RNA@layers$scale.data <- NULL
merged_mouse@neighbors <- list()
merged_mouse@graphs$RNA_nn <- NULL
merged_mouse@graphs$RNA_snn <- NULL

merged_mouse@meta.data <-
  merged_mouse@meta.data %>%
  select(individ_clusters, Sample_ID, cell_barcode)

format(object.size(merged_mouse), units = "Mb")

qs2::qs_save(merged_mouse, "b6_balbc_sobj.qs2")
```

## Make up cell barcode table
```{r make_cbt}
#| eval: false
cell_barcode_table <-
  merged_mouse@meta.data %>%
  as_tibble() %>%
  mutate(
    bam_file = if_else(
      Sample_ID == "S0066",
      "B6_chr19_scRNA.bam",
      "BALBc_chr19_scRNA.bam"
    ),
    strain = if_else(
      Sample_ID == "S0066",
      "B6",
      "BALBc"
    ),
    cell_group = paste0(strain, "_cluster_", individ_clusters)
  ) %>%
  select(cell_barcode, bam_file, cell_group)

qs2::qs_save(cell_barcode_table, "cell_barcode_table.qs2")
```

## Run scanBit on the data
```{r}
hg38_ref_fasta <- "mm10_chr19_plus.fa"

snp_tree <-
  get_snp_tree(
    cellid_bam_table = cell_barcode_table,
    temp_dir = "test/temp",
    ploidy = "mm10",
    output_dir = "test",
    output_base_name = "test_chr19",
    ref_fasta = hg38_ref_fasta,
    min_depth = 10,
    job_base = "two_sobj",
    min_snvs_per_cluster = 100,
    max_prop_missing_at_site = 0.75,
    cleanup = TRUE,
    job_scheduler = "bash",
    submit = TRUE,
    other_batch_options = c( # Just here as examples of things you might put
      "module purge",
      "module load miniforge3",
      'eval "$(conda shell.bash hook)"'
    )
  )
```

## Data for figshare
data/b6_balbc_sobj.qs2
data/cell_barcode_table.qs2
data/mm10_chr19_plus.fa
data/mm10_chr19_plus.fa.fai
data/BALBc_chr19_scRNA.bam
data/BALBc_chr19_scRNA.bam.bai
data/B6_chr19_scRNA.bam
data/B6_chr19_scRNA.bam.bai
data/test/mergedtest_chr19_c10.bcf
data/test/mergedtest_chr19_c10.bcf.csi